Revisiting Multi-Domain Machine Translation

### 2020-10-13 2020/tacl2020/final_multidomain.tex
BANK 1,2 -> LAW 1,2 table 4

\begin{table*}
  \centering% \small
  \begin{tabular}{|p{1.8cm}|*{10}{r|}} \hline
    % &&&&&& \\
    \hfill Set-up & \multicolumn{2}{c|}{Split} &  \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Merge} & \multicolumn{2}{c|}{Wrong} \\ % \hline
     Model \hfill & \multicolumn{2}{c|}{\domain{med} \footnotesize{(0.5 / 0.5)}} &  \multicolumn{2}{c|}{\domain{med} {\footnotesize (0.25 / 0.75)}} & \multicolumn{2}{c|}{\domain{law} {\footnotesize (0.5 / 0.5)}} & \multicolumn{2}{c|}{\domain{bank}+\domain{law}} &  \multicolumn{1}{c|}{\domain{rnd}} &  \multicolumn{1}{c|}{\domain{new}}\\ \hline
    & \domain{med}$_1$ & \domain{med}$_2$ & \domain{med}$_1$ & \domain{med}$_2$ &  \domain{bank}$_1$ & \domain{bank}$_2$ & \domain{bank} & \domain{law}   & \domain{all} & \domain{News} \\
    \system{FT-Full}      & -0.1 & -0.6 & \SW{-1.5} & -0.2& \SW{-2.3} & \SW{-5.1} &\SW{-1.6} & \SW{-1.4}& \SW{-19.6} & \SW{-3.3}\\% [32.5]
    \system{DC-Tag}     & -0.2 & -0.3& +\SB{0.1}  & +0.2& -0.4 & -0.4 & -0.5 & -0.4 & \SW{-13.4} & \SW{-1.7}\\% [35.9]
    \system{DC-Feat}    & -0.5 & 0.0 & +\SB{0.3}   & +0.3 & +0.3 & +0.3 & +0.3 & +0.1 & \SW{-14.2} &\SW{-1.8}\\ % [34.9] 
    \system{LDR}           & +0.1 & +0.1 & +0.4 & +0.4 & 0.0 &  0.0 &  0.0 & +0.1& \SW{-12.0} & \SW{-1.4}\\ % [37.0]
    \system{TTM} (*)        & -0.2 &  -0.2 & -0.2 & -0.2 & -0.3 &-0.3 &  0.0 & -0.3 & 0.0 & -0.1\\
%    \system{MDL Gated} & & & & & & & & &  \\
    \system{DM} (*)           & -0.3   & -0.3  & +0.4 & +0.4 & +0.3 & +0.3 & +0.9 & +0.1 & 0.0 &-0.9\\
    \system{ADM} (*)        & +0.6   & +0.6 & +0.4 & +0.4 & +0.4 & +0.4 &  +0.1 & -0.4 & 0.0&-0.2\\
    \revision{\system{FT-Res}}   & -0.1   & -0.4 & -0.3 &-0.3 & \SW{-2.2} & \SW{-2.9} & \SW{-2.4} & -\SW{3.2} & \SW{-13.3} & \SW{-3.0}\\ % [31.8]
    \system{MDL-Res}   & -0.2   & -0.1 & +\SB{0.2} &+0.0 & -0.9 & -0.9 & +0.7 & -0.3 & \SW{-18.6} & \SW{-1.3}\\ % [31.8]
    \system{WDCMT} (*)     & -0.0    & -0.0  & +0.2 & +0.2  & +0.8 & +0.8  & -0.4 & -0.8 & 0.0 & +0.2 \\
    \hline
  \end{tabular}
  \caption{Translation performance with variable domain definitions. In the Split/Merge experiments, we report BLEU differences for the related test set(s). Underline denotes significant loss when domains are changed wrt.\ the baseline situation; bold for a significant improvement over \system{FT-Full}; (*) tags systems ignoring test domains.
    \fyDone{Check wrong and significance of diff for ``old''}\fyDone{How about wrong ?}\jcDone{FTres results are odd... split LAW 0.5}
  }
  \label{tab:redomains}
\end{table*}

@@

The work presented in this paper was partially supported by the European Commission under contract H2020-787061 ANITA.
% This work was granted access to the HPC resources of [TGCC/CINES/IDRIS] under the allocation 20XX- [numéro de dossier] made by GENCI (Grand Equipement National de Calcul Intensif)
% The acknowledgements should go immediately before the references.  Do
% not number the acknowledgements section. Do not include this section
% when submitting your paper for review.

>>>>

\begin{table*}
  \centering% \small
  \begin{tabular}{|p{1.8cm}|*{10}{r|}} \hline
    % &&&&&& \\
    \hfill Set-up & \multicolumn{2}{c|}{Split} &  \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Merge} & \multicolumn{2}{c|}{Wrong} \\ % \hline
     Model \hfill & \multicolumn{2}{c|}{\domain{med} \footnotesize{(0.5 / 0.5)}} &  \multicolumn{2}{c|}{\domain{med} {\footnotesize (0.25 / 0.75)}} & \multicolumn{2}{c|}{\domain{law} {\footnotesize (0.5 / 0.5)}} & \multicolumn{2}{c|}{\domain{bank}+\domain{law}} &  \multicolumn{1}{c|}{\domain{rnd}} &  \multicolumn{1}{c|}{\domain{new}}\\ \hline
    & \domain{med}$_1$ & \domain{med}$_2$ & \domain{med}$_1$ & \domain{med}$_2$ &  \domain{law}$_1$ & \domain{law}$_2$ & \domain{bank} & \domain{law}   & \domain{all} & \domain{News} \\
    \system{FT-Full}      & -0.1 & -0.6 & \SW{-1.5} & -0.2& \SW{-2.3} & \SW{-5.1} &\SW{-1.6} & \SW{-1.4}& \SW{-19.6} & \SW{-3.3}\\% [32.5]
    \system{DC-Tag}     & -0.2 & -0.3& +\SB{0.1}  & +0.2& -0.4 & -0.4 & -0.5 & -0.4 & \SW{-13.4} & \SW{-1.7}\\% [35.9]
    \system{DC-Feat}    & -0.5 & 0.0 & +\SB{0.3}   & +0.3 & +0.3 & +0.3 & +0.3 & +0.1 & \SW{-14.2} &\SW{-1.8}\\ % [34.9] 
    \system{LDR}           & +0.1 & +0.1 & +0.4 & +0.4 & 0.0 &  0.0 &  0.0 & +0.1& \SW{-12.0} & \SW{-1.4}\\ % [37.0]
    \system{TTM} (*)        & -0.2 &  -0.2 & -0.2 & -0.2 & -0.3 &-0.3 &  0.0 & -0.3 & 0.0 & -0.1\\
%    \system{MDL Gated} & & & & & & & & &  \\
    \system{DM} (*)           & -0.3   & -0.3  & +0.4 & +0.4 & +0.3 & +0.3 & +0.9 & +0.1 & 0.0 &-0.9\\
    \system{ADM} (*)        & +0.6   & +0.6 & +0.4 & +0.4 & +0.4 & +0.4 &  +0.1 & -0.4 & 0.0&-0.2\\
    \revision{\system{FT-Res}}   & -0.1   & -0.4 & -0.3 &-0.3 & \SW{-2.2} & \SW{-2.9} & \SW{-2.4} & -\SW{3.2} & \SW{-13.3} & \SW{-3.0}\\ % [31.8]
    \system{MDL-Res}   & -0.2   & -0.1 & +\SB{0.2} &+0.0 & -0.9 & -0.9 & +0.7 & -0.3 & \SW{-18.6} & \SW{-1.3}\\ % [31.8]
    \system{WDCMT} (*)     & -0.0    & -0.0  & +0.2 & +0.2  & +0.8 & +0.8  & -0.4 & -0.8 & 0.0 & +0.2 \\
    \hline
  \end{tabular}
  \caption{Translation performance with variable domain definitions. In the Split/Merge experiments, we report BLEU differences for the related test set(s). Underline denotes significant loss when domains are changed wrt.\ the baseline situation; bold for a significant improvement over \system{FT-Full}; (*) tags systems ignoring test domains.
    \fyDone{Check wrong and significance of diff for ``old''}\fyDone{How about wrong ?}\jcDone{FTres results are odd... split LAW 0.5}
  }
  \label{tab:redomains}
\end{table*}

@@

The work presented in this paper was partially supported by the European Commission under contract H2020-787061 ANITA.

This work was granted access to the HPC resources of [TGCC/CINES/IDRIS] under the allocation 2020- [AD011011270] made by GENCI (Grand Equipement National de Calcul Intensif)
% The acknowledgements should go immediately before the references.  Do
% not number the acknowledgements section. Do not include this section
% when submitting your paper for review.
